### 2024-06-06 Scripts/Scripts-collection.Rmd
Update Scripts-collection.Rmd

df_diversity  <- read.csv(r"(G:\Bio-Analysis\Python\Vscode\Task01-NEW\Data_submission\GitHub_repository\Data_repository\Supplementary_figures\alpha_diversity-comparison-pneumonia_vs_no_pneumonia.csv)",header = TRUE)
df_merged_subset$Diagnosed.Pneumonia   <- factor(df_merged_subset$Diagnosed.Pneumonia,levels = c("No","Yes"))

@@

df_arg_abundance  <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\argtypes-pneumonia_vs_nopneumonia.csv)",header = TRUE)
df_arg_abundance$totoal_arg_abundance_log10 <- log10(df_arg_abundance$totoal_arg_abundance)
my_comparisons <- list(c("No",'Yes'))
p_arg_abundance <- ggplot(df_arg_abundance, aes(x=Diagnosed.Pneumonia,y=totoal_arg_abundance_log10,fill=Diagnosed.Pneumonia)) +
  stat_boxplot(geom = "errorbar",width=0.15)+
  geom_boxplot(size=0.5 ) + #theme_classic2() +
  geom_line(size=0.3) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800")) +
  scale_x_discrete(labels = c("No Pneumonia","Pneumonia")) +
  stat_compare_means(label.y = 3.0,comparisons = my_comparisons,label = "p.signif",size=7,bracket.size = 0.5) +
  stat_compare_means(label.y = 3.8,label.x = 1,size=8) + 
  labs(x = NULL, y = "Total ARG abundance (log10)") +
  theme_pubr(base_size = 20, border =F,legend = "none")
ggpar(p_arg_abundance,x.text.angle = 30,legend = 'none')

@@

@@

df_profiles = read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\microbiota-pneumonia-species_phyloseqized.csv)",header = FALSE)
sampleid2site = read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\metadata-pneumonia-sampleid2site.csv)",header = TRUE)
df_arrows <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\MDS_metrics-bray-specie_pneumonia-arrows_coordinates.csv)')

#otu-like data reformat 
otu_metaphlan <- as.matrix(df_profiles[2:nrow(df_profiles),2:ncol(df_profiles)]) # otu matrix can't have any character-like data, you have to use index to remove it
class(otu_metaphlan) <- "numeric" # convert the datatype of the matrix into "numeric"
otu_metaphlan <- otu_metaphlan*1000000
rownames(otu_metaphlan) <- df_profiles[2:nrow(df_profiles),1]
colnames(otu_metaphlan) <- df_profiles[1,2:ncol(df_profiles)]

OTU = otu_table(otu_metaphlan,taxa_are_rows = TRUE)
rownames(sampleid2site) <- sampleid2site$SampleID # you have to re-assign the rownames of meta-data, or you will run into a problem: "invalid “phyloseq” object: Component sample names do not match"
sam_data = sample_data(sampleid2site)
physeq_profiles = phyloseq(OTU,sam_data) 
target_dist_methods <- c('bray')
for( i in target_dist_methods ){
  target_dist <- distance(physeq_profiles, method=i)
  target_MDS_metrics <- ordinate(physeq_profiles, "MDS", distance=target_dist)
  df_metrics <- data.frame(target_MDS_metrics[["vectors"]])
  df_metrics_filter <- df_metrics[,1:2]

  # Merge df_metrics_filter and sampleid2site on the index
  df_metrics_filter <- merge(df_metrics_filter, sampleid2site, by="row.names", all.x=TRUE)
  df_metrics_filter  <- df_metrics_filter[,c(4,2,3,5)]
}

df_arrows$variable <- str_split(df_arrows$variable, "__", simplify = TRUE)[,2]
df_arrows$variable  <- str_replace_all(df_arrows$variable, "_", " ")
df_arrows$variable  <- str_replace_all(df_arrows$variable, " group", " ")
df_distance_bray$Axis.2 <- df_distance_bray$Axis.2*-1
df_arrows$Axis.2 <- df_arrows$Axis.2*-1

plots <- ggscatter(df_distance_bray,
                   x = "Axis.1", 
                   y = "Axis.2",
                   color = "SamplingSite",
                   #shape = "SamplingSite",
                   size=6,
                   # palette = c( "#FC4E07","#00AFBB", "#E7B800"), #color1
                   palette = c("#e64833", "#01a188", "#3e5386"), #color2
                   # palette = c("#c23726", "#e3e3e3", "#0036fc"),  #palette2
                   # palette = c( "#010101","#fe0000", "#0037fe"), #palette4
                   #palette = c("#c23726", "#5a5a5a", "#2c83c6"),
                   #palette = c("#7152a9", "#ffc376", "#eb7600"),
                   margin.plot = "boxplot",
                   ggtheme = theme_pubr(),
                   #margin.params = list(fill="SamplingSite",size=0.36),
                   legend = 'right') + 
  geom_segment(data = df_arrows,
               x = 0, y = 0, alpha = 0.7,
               mapping = aes(xend = Axis.1, yend = Axis.2),
               color = 'black',size=0.1,
               # Add arrow head
               arrow = arrow(length = unit(3, "mm"))) +
  geom_label(data = df_arrows, aes(label = variable),color='black',alpha=0.7,size=7,label.size =0.01) 
ggpar(plots,
      xlab = "MDS1 (27.6%)",
      ylab = "MDS2 (16.6%)") + theme_pubr(base_size = 24,border = T,legend = 'none')

@@

df_distance_bray_species_pneumonia <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\MDS_metrics-bray+species_abundance-species_pneumonia.csv)')
df_distance_bray_species_pneumonia$variable <- str_split(df_distance_bray_species_pneumonia$variable, "__", simplify = TRUE)[,2]
df_distance_bray_species_pneumonia$variable  <- str_replace_all(df_distance_bray_species_pneumonia$variable, "_", " ")
df_distance_bray_species_pneumonia$variable  <- str_replace_all(df_distance_bray_species_pneumonia$variable, " group", " ")
df_distance_bray_species_pneumonia$Axis.2 <- df_distance_bray_species_pneumonia$Axis.2*-1

@@

patientids <- c('P68','P23')
df_abundance <- read.csv(paste("LRT_microbiomes_critical_illness\Data_repository\Main_figures/microbiota-individual_patient/",
                               patientid,"-metaphlan3-species_microbiota.csv",sep=""))

@@

>>>>

df_diversity  <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\alpha_diversity-comparison-pneumonia_vs_no_pneumonia.csv)",header = TRUE)
df_merged_subset$Diagnosed.Pneumonia   <- factor(df_merged_subset$Diagnosed.Pneumonia,levels = c("No","Yes"))

@@

df_arg_abundance  <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\argtypes-comparison-pneumonia_vs_nopneumonia.csv)",header = TRUE)
df_arg_abundance$totoal_arg_abundance_log10 <- log10(df_arg_abundance$totoal_arg_abundance)
my_comparisons <- list(c("No",'Yes'))
p_arg_abundance <- ggplot(df_arg_abundance, aes(x=Diagnosed.Pneumonia,y=totoal_arg_abundance_log10,fill=Diagnosed.Pneumonia)) +
  stat_boxplot(geom = "errorbar",width=0.15)+
  geom_boxplot(size=0.5 ) + #theme_classic2() +
  geom_line(size=0.3) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800")) +
  scale_x_discrete(labels = c("No Pneumonia","Pneumonia")) +
  stat_compare_means(label.y = 3.0,comparisons = my_comparisons,label = "p.signif",size=7,bracket.size = 0.5) +
  stat_compare_means(label.y = 3.8,label.x = 1,size=8) + 
  labs(x = NULL, y = "Total ARG abundance (log10)") +
  theme_pubr(base_size = 20, border =F,legend = "none")
ggpar(p_arg_abundance,x.text.angle = 30,legend = 'none')

@@

### Figure 2
### --------------------------------------------------------------------------------------------------------------------------------------------

@@

df_distance_bray <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\MDS_metrics-bray-species_profiles_pneumonia.csv)')  # save in the same file 'MDS_metrics-bray-species_profiles_pneumonia.txt'
df_arrows <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\MDS_metrics-bray-specie_pneumonia-arrows_coordinates.csv)') # save in the same file 'MDS_metrics-bray-species_profiles_pneumonia.txt'
df_arrows$variable <- str_split(df_arrows$variable, "__", simplify = TRUE)[,2]
df_arrows$variable  <- str_replace_all(df_arrows$variable, "_", " ")
df_arrows$variable  <- str_replace_all(df_arrows$variable, " group", " ")

#remove plot direction
df_distance_bray$Axis.2 <- df_distance_bray$Axis.2*-1
df_arrows$Axis.2 <- df_arrows$Axis.2*-1

plots <- ggscatter(df_distance_bray,
                   x = "Axis.1", 
                   y = "Axis.2",
                   color = "SamplingSite",
                   #shape = "SamplingSite",
                   size=6,
                   # palette = c( "#FC4E07","#00AFBB", "#E7B800"), #color1
                   palette = c("#e64833", "#01a188", "#3e5386"), #color2
                   # palette = c("#c23726", "#e3e3e3", "#0036fc"),  #palette2
                   # palette = c( "#010101","#fe0000", "#0037fe"), #palette4
                   #palette = c("#c23726", "#5a5a5a", "#2c83c6"),
                   #palette = c("#7152a9", "#ffc376", "#eb7600"),
                   margin.plot = "boxplot",
                   ggtheme = theme_pubr(),
                   #margin.params = list(fill="SamplingSite",size=0.36),
                   legend = 'right') + 
  geom_segment(data = df_arrows,
               x = 0, y = 0, alpha = 0.7,
               mapping = aes(xend = Axis.1, yend = Axis.2),
               color = 'black',size=0.1,
               # Add arrow head
               arrow = arrow(length = unit(3, "mm"))) +
  geom_label(data = df_arrows, aes(label = variable),color='black',alpha=0.7,size=7,label.size =0.01)

ggpar(plots,
      xlab = "MDS1 (27.6%)",
      ylab = "MDS2 (16.6%)") + theme_pubr(base_size = 24,border = T,legend = 'none')

@@

df_distance_bray_species_pneumonia <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\MDS_metrics-bray+species_abundance-species_pneumonia.csv)') # save in the same file 'MDS_metrics-bray-species_profiles_pneumonia.txt'
df_distance_bray_species_pneumonia$variable <- str_split(df_distance_bray_species_pneumonia$variable, "__", simplify = TRUE)[,2]
df_distance_bray_species_pneumonia$variable  <- str_replace_all(df_distance_bray_species_pneumonia$variable, "_", " ")
df_distance_bray_species_pneumonia$variable  <- str_replace_all(df_distance_bray_species_pneumonia$variable, " group", " ")
df_distance_bray_species_pneumonia$Axis.2 <- df_distance_bray_species_pneumonia$Axis.2*-1

@@

patientids <- c('P68','P23')
df_abundance <- read.csv(paste("LRT_microbiomes_critical_illness\Data_repository\Main_figures",
                               patientid,"-metaphlan3-species_microbiota.csv",sep="")) # save in the same file 'pid_individual-metaphlan3-species_microbiota.txt'

@@

```{r Fig 2f}

df_argtypes_collection <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\argtypes-collection_all_sites-pneumonia_patients.csv)")
df_argtypes_collection2 <- arrange(df_argtypes_collection,SamplingSite)
my_comparisons <- list( c("HospitalA", "HospitalB"), c("HospitalA", "HospitalC"), c("HospitalB", "HospitalC") )

#plot for 'multidrug'
ggboxplot(df_argtypes_collection2, x="SamplingSite", y="multidrug",
          color = "SamplingSite", palette =c("#f93800", "#007a8b","#ffb500"),
          add = "jitter",add.params = list(size = 2, alpha = 0.5))  +
  stat_boxplot(mapping = aes(color=SamplingSite),geom = "errorbar",width=0.1)  +
  geom_boxplot(aes(color=SamplingSite), lwd = 0.7,geom = "errorbar",) +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=5,
                     vjust=.15,tip.length= c(0,0,0)) + 
  yscale("log10", .format = F)  + 
  labs(x=NULL,y='ARG abundance',) +  ggtitle('Multidrug') +
  theme_pubr(base_size = 18,legend ='none',x.text.angle = 30) +
  ggeasy::easy_center_title()

#plot for 'aminoglycoside'
ggboxplot(df_argtypes_collection2, x="SamplingSite", y="aminoglycoside",
                             color = "SamplingSite", palette =c("#f93800", "#007a8b","#ffb500"),
                             add = "jitter",add.params = list(size = 2, alpha = 0.5))  +
  stat_boxplot(mapping = aes(color=SamplingSite),geom = "errorbar",width=0.1)  +
  geom_boxplot(aes(color=SamplingSite), lwd = 0.7,geom = "errorbar",) +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=5,
                     vjust=.15,tip.length= c(0,0,0)) + 
  yscale("log10", .format = F)  + 
  labs(x=NULL,y='ARG abundance',) +  ggtitle('Aminoglycoside') +
  theme_pubr(base_size = 18,legend ='none',x.text.angle = 30) +
  ggeasy::easy_center_title()

#plot for 'beta.lactam'
ggboxplot(df_argtypes_collection2, x="SamplingSite", y="beta.lactam",
          color = "SamplingSite", palette =c("#f93800", "#007a8b","#ffb500"),
          add = "jitter",add.params = list(size = 2, alpha = 0.5))  +
  stat_boxplot(mapping = aes(color=SamplingSite),geom = "errorbar",width=0.1)  +
  geom_boxplot(aes(color=SamplingSite), lwd = 0.7,geom = "errorbar",) +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=5,
                     vjust=.15,tip.length= c(0,0,0)) + 
  yscale("log10", .format = F)  +
  labs(x=NULL,y='ARG abundance',) +  ggtitle('Beta-lactam') +
  theme_pubr(base_size = 18,legend ='none',x.text.angle = 30) +
  # theme(strip.text.x = element_text(size = 13.5)) +
  ggeasy::easy_center_title()
